DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-01 paper/background.tex
background revision (WIP)

The use of neural networks for end-to-end control of autonomous
driving was first demonstrated in late 1980s~\cite{Pomerleau1989}, but
its success has been limited at the time as its performance was not
sufficient enough.

@@

>>>>

The use of neural networks for end-to-end control of autonomous
driving was first demonstrated in late 1980s~\cite{Pomerleau1989},
using a small fully connected neural network; and subsequently in a
DARPA Autonomous Vehicle (DAVE) project in early
2000s~\cite{LeCun:04}, using a 6 layer convolutional neural network
(CNN); and most recently in NVIDIA's DAVE-2
project~\cite{Bojarski2016}, using 9 layer CNN. In all these projects,
the neural network models take raw image pixels as input and directly
produce steering control commands bypassing all intermediary steps and
hand-written rules in conventional robotics control approach. The
NVIDIA's latest effort reports that their trained CNN successfully 
self-drive their modified cars in public roads without human
intervention~\cite{Bojarski2016}.

@@

Recent successes in AI, including the NVIDIA's DAVE-2 showing, are due
in large part to the increased computing capability of computers,
which affored researchers to train ever deeper networks with high
accuracy. In automotive systems,
